---
title: "Tara Oceans post analysis"
author: "Aram Avila-Herrera"
date: "`r Sys.Date()`"
output:
    html_document:
        toc: true
...


```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = '#>', width = 125)
options(width=125)
```

## load results

```{r}
library(dplyr)
library(readr)
library(magrittr)
library(tidyr)

res_df = read_tsv('./results_final.tsv',
                  col_types = 'ccccddiddddddddidd'
                  )
```

## summaries

### Size fraction groups

```{r}
unique(res_df$fraction_cat)
```

### Number of tests

#### total

```{r}
nrow(res_df)
```

#### by size fraction groups

```{r}
res_df %>% count(fraction_cat)
```

#### by term (coefficient name in glm)

```{r}
res_df %>% count(term)
```

#### by PHENONAME (environmental variable being tested)

```{r}
res_df %>% count(PHENONAME)
```

#### by size fraction group and PHENONAME

```{r}
res_df %>% count(fraction_cat, PHENONAME)
```

## significant tests (`p_adj_fdr < 0.05`)

#### by size fraction and FUNKID

```{r}
res_df %>% filter(p_adj_fdr < 0.05) %>%
           count(fraction_cat, FUNKID, sort = TRUE)
```

#### by size fraction group, FUNKID, and PHENONAME

```{r}
res_df %>% filter(p_adj_fdr < 0.05) %>%
           count(fraction_cat, FUNKID, PHENONAME, sort = TRUE)
```

## $\Delta$BIC

```{r}
# extract "no predictors" model results
nop_df = res_df %>% filter(PHENONAME == 'latitude_start') %>%
                    select(fraction_cat, FUNKID, BIC_nop = BIC)

# merge with results to get change in BICs (delBIC)
res_df %<>% full_join(nop_df) %>% mutate(delBIC = BIC_nop - BIC) %>%
            select(fraction_cat, FUNKID, term, PHENONAME, delBIC, p_adj_fdr,
                   BIC, BIC_nop
                   ) %>%
            arrange(p_adj_fdr, desc(delBIC))

res_df %>% select(-BIC, -BIC_nop)

# significant tests where richer model fits better
res_df %>% filter(p_adj_fdr < 0.05, delBIC > 6) %>%
           count(fraction_cat, sort = TRUE)
```

#### By size fraction group and FUNKID

```{r}
res_df %>% filter(p_adj_fdr < 0.05, delBIC > 6) %>%
           count(fraction_cat, FUNKID) %>% ungroup() %>% arrange(desc(n))
```

#### By FUNKID alone

```{r}
res_df %>% filter(p_adj_fdr < 0.05, delBIC > 6) %>%
           count(FUNKID, sort = TRUE)
```

#### By size fraction group and PHENONAME

```{r}
res_df %>% filter(p_adj_fdr < 0.05, delBIC > 6) %>%
           count(fraction_cat, PHENONAME) %>% ungroup() %>%
           arrange(desc(n))
```

#### By PHENONAME alone

```{r}
res_df %>% filter(p_adj_fdr < 0.05, delBIC > 6) %>%
           count(PHENONAME, sort = TRUE)
```

#### X6_49036

```{r}
res_df %>% filter(FUNKID == 'X6_49036', p_adj_fdr < 0.05) %>%
           select(PHENONAME, fraction_cat,
                  p_adj_fdr, delBIC, BIC, BIC_nop
                  )
```
